---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(lubridate)
library(tigris)
```

Interviews started in January of 2017 and continued through May 2017
Toilet qustion past 3 months
Mice and rats past 3 months

cockroaches past month

Therefore 311 data October 2016-May 2017
department housing preservation
10/01/2016 12:00:00 AM
06/01/2017 12:00:00 AM

Complaint Type %in% c("HEAT/HOT WATER", "FLOORING/STAIRS", "PLUMBING", "UNSANITARY CONDITION", "PAINT/PLASTER", "WATER LEAK")

```{r, eval=FALSE}
# df0 <- read_csv("../../data/input/311_Service_Requests_from_2010_to_Present.csv")
rm(list = ls())
df0 <- read_csv("../../data/input/311_Service_Requests_from_2010_to_Present.csv") %>%
        select(`Created Date`, `Complaint Type`, Descriptor, `Incident Zip`, 
               `Incident Address`, `Street Name`, Borough, City, Latitude, Longitude, 
                Location) %>%
        mutate(issue_stairway = `Complaint Type` == "FLOORING/STAIRS" & 
                                 Descriptor == "STAIRS",
               issue_floors = `Complaint Type` == "FLOORING/STAIRS" & 
                               Descriptor == "FLOOR",
               issue_toilet = `Complaint Type` == "PLUMBING" & 
                               Descriptor == "TOILET",
               issue_heat = `Complaint Type` == "HEAT/HOT WATER" & 
                             Descriptor == "APARTMENT ONLY",
               issue_pests = `Complaint Type` == "UNSANITARY CONDITION" & 
                             Descriptor == "PESTS",
               issue_plasterpaint = `Complaint Type` == "PAINT/PLASTER" & 
                                     Descriptor %in% c("CEILING", "WALL"),
               issue_leak = `Complaint Type` == "WATER LEAK",
               # datetime formatted to confirm proper timeframe represented
               `Created Date` = mdy_hms(`Created Date`)) %>% 
        filter(select(., starts_with("issue")) %>% rowSums() == 1) %>%
        filter(!is.na(Location)) %>%
          # confirm that a residence only reports complain once in dataset
        group_by(`Complaint Type`, Descriptor, Latitude, Longitude, 
                 Borough, City, `Incident Zip`) %>%
        summarise_at(vars(starts_with("issue")), funs(max(.))) 
```

use [census geolocate api](https://www.census.gov/geo/maps-data/data/geocoder.html) to get the census code associated with coordinates                  
note: [how to interpret census code](http://proximityone.com/geo_tracts.htm)      
```{r, eval=FALSE}
# note: this code takes approx 6 hours to run
start_time <- Sys.time()
df1 <- df0 %>%
       mutate(census_code = map2(.x = Latitude, .y = Longitude, .f = call_geolocator_latlon))
stop_time <- Sys.time()

write_csv(df1, "../../data/output/nyc311/01-nyc311_complaintXcoordinates.csv")
saveRDS(df1, "../../data/output/nyc311/01-nyc311_complaintXcoordinates.rds")
```

```{r}
df1 <-  read_rds("../../data/output/nyc311/01-nyc311_complaintXcoordinates.rds") %>%
        mutate(census_code = as.character(census_code),
               state_code = str_sub(census_code, 1, 2),
               county_code = str_sub(census_code, 3, 5),
               census_tract = str_sub(census_code, 6, 11))

# how to access other meta information in census_code
               # state_code = str_sub(census_code, 1, 2),
               # county_code = str_sub(census_code, 3, 5),
               # census_tract = str_sub(census_code, 6, 11),
               # census_block = str_sub(census_code, 12, 15),
```

Aim: Now that I have census tract information about each complaint, I want to link census tract to 
Public Use Microdata Areas (PUMAs) because these areas approximate to sub-boroughs. Once I know the sub-borough of each complaint, then I can link 311 data to NYCHVS data.

Here is the webpage storing the text file that links [Census Tract to PUMAs](https://www.census.gov/geo/maps-data/data/centract_rel.html)
```{r}
tract2pumas <- read_csv("https://www2.census.gov/geo/docs/maps-data/data/rel/2010_Census_Tract_to_2010_PUMA.txt")

write_csv(tract2pumas, "../../data/input/linking/2010_Census_Tract_to_2010_PUMA.csv")
```

join 311 data with pumas data
```{r}
df1 <- left_join(x = df1, 
                 y = tract2pumas, 
                 by = c("state_code" = "STATEFP", 
                        "county_code" = "COUNTYFP",
                        "census_tract" = "TRACTCE")) 
```

prepare 311 data go be joined with nychvs data
```{r}
df2 <- df1 %>%
       mutate(geo_id2 = paste0(state_code, PUMA5CE)) %>%
       group_by(geo_id2) %>%
       summarise_at(vars(starts_with("issue")), funs(sum(.))) %>%
       arrange(geo_id2)
```

```{r}
write_csv(df2, "../../data/output/nyc311/02-nyc311_complaintXsubboro.csv")
saveRDS(df2, "../../data/output/nyc311/02-nyc311_complaintXsubboro.rds")
```

********************************************************************************
```{r}
knitr::opts_chunk$set(eval = FALSE)
```

check recode of issue_stairway variable
```{r issue_stairway}
df %>%
group_by(`Complaint Type`, Descriptor, issue_stairway) %>%
summarise(sum(issue_stairway))
```

check recode of issue_floors variable
```{r issue_floors}
df %>%
group_by(`Complaint Type`, Descriptor, issue_floors) %>%
summarise(sum(issue_floors))
```

check recode of issue_toilet
```{r issue_toilet}
df %>%
group_by(`Complaint Type`, Descriptor, issue_toilet) %>%
summarise(sum(issue_toilet))
```

check recode of issue_heat 
```{r issue_heat}
df %>%
group_by(`Complaint Type`, Descriptor, issue_heat) %>%
summarise(sum(issue_heat))
```

check recode of issue_pests
```{r issue_pests}
df %>%
group_by(`Complaint Type`, Descriptor, issue_pests) %>%
summarise(sum(issue_pests))
```

check recode of issue_plasterpaint
```{r issue_plasterpaint}
df %>%
group_by(`Complaint Type`, Descriptor, issue_plasterpaint) %>%
summarise(sum(issue_plasterpaint))
```

check recode of issue_leak
```{r issue_leak}
df %>%
group_by(`Complaint Type`, Descriptor, issue_leak) %>%
summarise(sum(issue_leak))
```

