---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(readxl)
nychvs2017 <- "../../data/input/nychvs/NYCHVS 2017 Occupied File for ASA Challenge_CSV.csv"
```

```{r codebook}
codebook <- read_csv(nychvs2017)[1,] %>% 
            t() %>% 
            as.matrix() %>% 
            as_tibble(rownames = NA)
```

```{r recode_vars}
df <- read_csv(nychvs2017)[-1,] %>%
      mutate(issue_stairway = `_f1` == 1 | `_f2` == 1,
             issue_floors = `_g12` == 1 | `_g3` == 1 | `_g4` == 1,
             renter = `_9a` == 9,
             issue_toilet =  `_25c` == 1, 
             issue_heat = `_32a` == 0,
             issue_pests = `_35a` == 1 | `_35b` %in% 2:4,
             issue_plasterpaint = `_37a` == 0,
             issue_leak = `_38a` == 1,
             housing_public = csrr == 5) %>%
      select(seqn, borough, sub, sba, geo_id2, starts_with("issue"), 
             renter, housing_public, hhweight, starts_with("FW")) %>% 
      modify_at(c("hhweight", paste0("FW", 1:80)), as.integer) 
```

join in additional information about sub-boroughs (ie pumas)      
This dataset containing sub-borough information came from Baruch College's The William & Anita Newman Library [Resourch Guide on New York City Data](https://www.baruch.cuny.edu/confluence/display/geoportal/NYC+Geographies)
```{r}
pumas <- read_excel("../../data/input/linking/nyc_puma_neighborhood.xls")

df <- left_join(df, pumas, by = c("geo_id2" = "PUMA5ID")) %>%
      rename(borough_name = Borough) %>%
      select(seqn, borough, sub, sba, geo_id2, borough_name:PUMA_2010, 
             starts_with("issue"), renter, housing_public, 
             hhweight, starts_with("FW"))
```

```{r}
write_csv(df, "../../data/output/nychvs/nychvs2017.csv")
saveRDS(df, "../../data/output/nychvs/nychvs2017.rds")
```

********************************************************************************
```{r}
knitr::opts_chunk$set(eval = FALSE)
```

check recode of issue_stairway variable
```{r issue_stairway}
# check issue_stairway
table(df$`_f1`, df$issue_stairway, useNA = "ifany")
table(df$`_f2`, df$issue_stairway, useNA = "ifany")
table(df$`_f1`, df$`_f2`, useNA = "ifany")
```

check recode of issue_floors variable
```{r issue_floors}
# check issue_stairway
table(df$`_g12`, df$issue_floors, useNA = "ifany")
table(df$`_g3`, df$issue_floors, useNA = "ifany")
table(df$`_g4`, df$issue_floors, useNA = "ifany")
```

check recode of renter variable
```{r renter}
# check variable recode
table(df$`_9a`, df$renter, useNA = "ifany")
# check how 2 variables about rental status relate to one another
table(df$`_9a`, df$`_9c`, useNA = "ifany")
```

check recode of issue_toilet
```{r issue_toilet}
table(df$`_25c`, df$issue_toilet, useNA = "ifany")
```

check recode of issue_heat 
```{r issue_heat}
# look at 2 variables related to heat
table(df$`_32b`, df$`_32a`, useNA = "ifany")
# recode
table(df$`_32a`, df$issue_heat, useNA = "ifany")
```

check recode of issue_pests
```{r issue_pests}
table(df$`_35a`, df$`_35b`, useNA = "ifany")

table(df$`_35a`, df$issue_pests, useNA = "ifany")
table(df$`_35b`, df$issue_pests, useNA = "ifany")
```

check recode of issue_plasterpaint
```{r issue_plasterpaint}
table(df$`_37a`, df$issue_plasterpaint, useNA = "ifany")
```

check recode of issue_leak
```{r issue_leak}
table(df$`_38a`, df$issue_leak, useNA = "ifany")
```

check recode of issue_leak
```{r housing_public}
table(df$csrr, df$housing_public)
```

explore relationship between sub-borough-area & geoid2
```{r}
sba <- df %>%
       group_by(sba, geo_id2) %>%
       summarise() %>%
       arrange(geo_id2)
```

check that the names sub-boroughs from joined dataset make sense
```{r}
df %>%
group_by(sba, SubBoroNum, SubBoroNam) %>%
summarise() %>%
arrange(sba) %>%
View()
```

